Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-06-04 aosd13/paperBody.tex
Cite Henglein's related papers

% Klaus: I think this is not that relevant for ICSE
%\citet{Henglein10} present an embedding of the relational algebra in Haskell.
%Queries are not reified in their approach, but due to a particularly sophisticated
%representation of multisets it is possible to execute some queries containing
%cross-products using faster equi-joins.

>>>>

% Klaus: I think this is not that relevant for ICSE
\citet{Henglein2010optimizing} and \citet{Henglein2010generic} embed relational algebra in
Haskell. Queries are not reified in their approach, but due to a particularly
sophisticated representation of multisets it is possible to execute some queries
containing cross-products using faster equi-joins. While their approach appears
to not rely on non-confluent rewriting rules and hence appears more robust, it
is not yet clear how to incorporate other optimizations.
